Bayesian exponential random graph modeling of KWL Burial network

### 2020-12-11 analysis/paper/paper.Rmd
edit conclusion and split code for sensitivity test to two

This case study highlights the methodological improvement that Bayesian inference on ERGM can inform and enhance studies in rational data in archaeology. A Bayesian framework reduced the effects of small sample size or missing data commonly present in archaeological data by incorporating prior information and MCMC estimations. Moreover, the interrelations indicated by the probabilistic inference provide robust results, allowing in-depth discussion for the dynamic processes of relationship formation and their underlying factors to reflect the historical trajectories of sociocultural phenomena. This approach can be applied to a wide range of relational data in archaeology to examine the formation of relationships and give an insight into the study of social structure in general.

>>>>

This case study highlights the methodological improvement that Bayesian inference on ERGM can inform and enhance studies in rational data in archaeology. A Bayesian framework can reduce the effects of small sample size or missing data commonly present in archaeological data by incorporating prior information and MCMC estimations. Moreover, probabilistic inference provides robust results of interrelations that are not statistically tested by traditional network approaches. Bayesian network modeling can be applied to a wide range of archaeological data to examine the formation of relationships. This allows in-depth discussion of dynamic processes of relationship formation and their underlying factors that are informative of historical trajectories or socio-cultural phenomena.
